\chapter*{ABSTRACT}

ASEE - Algorithmic Stock Exchange Engine is a project aimed at creating a user-friendly and efficient tool for backtesting trading strategies. This report presents the design and implementation of the application and demonstrates its capabilities through a series of experiments. We show that the app can successfully simulate a wide range of trading strategies and provide useful insights for traders and investors. Our results suggest that the ASEE is a promising tool for those interested in algorithmic trading and quantitative finance.

ASEE is a comprehensive research project aimed at developing a platform for creating, backtesting and deploying trading strategies based on various technical indicators. The project aims to provide a framework for traders to test their trading ideas, evaluate their performance and optimize them by selecting custom lookback days and  breakout percentages. The app is designed to be user-friendly and accessible to traders of all levels of expertise, providing them with the tools to create and test various trading strategies based on their specific requirements.

The research project is conducted with the aim of identifying and evaluating the effectiveness of various technical indicators and trading strategies in different market conditions. The project uses historical market data to backtest various trading strategies and evaluate their performance. The research aims to identify the most effective strategies based on different criteria such as risk-adjusted returns, volatility, and drawdowns.

The project also aims to analyze the impact of news and other fundamental factors on the performance of trading strategies.

ASEE is a significant contribution to the field of quantitative trading, providing traders with a powerful tool to develop and test various trading strategies. The research conducted as part of this project is expected to provide valuable insights into the effectiveness of different technical indicators and trading strategies in different market conditions. Overall, ASEE is an innovative and practical solution for traders looking to improve their trading performance and gain a competitive edge in the financial markets.

\cleardoublepage
