\thispagestyle{empty}

\setcounter{page}{3}

\chapter*{Declaration of Authorship}

\vspace{1cm}

\noindent 
We, \textbf{Avantika Modi, Hriday Gupta}, declare that the work presented in ``\textbf{ASEE - Algorithmic Stock Exchange Engine}" is our own. We confirm that:

\medskip

\begin{itemize} 
    \item This work was completed entirely while in candidature for B.Tech. degree at Indian Institute of Information Technology, Lucknow.
    
    \medskip
    
    \item Where we have consulted the published work of others, it is always cited.
    
    \medskip
    
    \item Wherever we have cited the work of others, the source is always indicated. Except for the aforementioned quotations, this work is solely our work.
    
    \medskip
    
    \item I have acknowledged all major sources of information.
\end{itemize}

\vspace{2cm}

\noindent Signed: \hspace{0.4cm}Avantika Modi \hspace{0.4cm} Hriday Gupta\\

\hspace{1.5cm}(Author1) \hfill (Author2) \hfill (Author3) \hfill (Author4)
\rule[0.5em]{33em}{0.5pt} 
 
\noindent Date: 26th April, 2023\\
\rule[0.5em]{33em}{0.5pt}

\cleardoublepage

\chapter*{CERTIFICATE}

This is to certify that the work entitled ``\textbf{ASEE - Algorithmic Stock Exchange Engine}" submitted by \textbf{Avantika Modi, Hriday Gupta} who got their name registered on \textbf{\;\;\; Jul 2020} for the award of B.Tech. degree at Indian Institute of Information Technology, Lucknow is absolutely based upon their own work under the supervision of \textbf{Dr. Vishal Krishna Singh}, Department of Computer Science and Artificial Intelligence, Institute of Information Technology, Lucknow - 226 002, U.P., India and that neither this work nor any part of it has been submitted for any degree/diploma or any other academic award anywhere before.  

\vspace{4cm}

\begin{center}
    Dr. Vishal Krishna Singh

    Department of Computer Science and Artificial Intelligence 

    Institute of Information Technology, Lucknow 

    Pin - 226002, INDIA 
\end{center}
